Supplementary material to `Adaptive group-regularized logistic elastic net regression'

### 2019-12-02 docs/manuscript.Rnw
merged old versions from onedrive

	In addition to simulations from the correct model, i.e., model

>>>>

	In addition to simulations from the correct model, i.e., model 
	(\ref{eq:enmodel2}), we simulated from an incorrect model to investigate 
	the performance of \texttt{gren} under model misspecification. We investigated
	both link misspecification and non-linear feature effects misspecification. 
	The details of the simulations and detailed results are given in SM Section 
	\ref{sm-sec:modelmisspecification}. In all investigated Scenarios 
	\texttt{gren} outperformed the regular elastic net in terms of predictive 
	performance; an indication that \texttt{gren} is somewhat robust to model
	misspecification.

### 2019-12-02 docs/supplement.Rnw
merged old versions from onedrive

  \subsection{Model misspecification}
  To assess the effects of model misspecification we conducted a series of 
  simulations under different modes of misspecification and simulation settings.
  We investigate model misspecification by comparing \texttt{gren} to the
  regular elastic net.
  To investigate the effect of misspecifying the link function, we simulated
  according to Scenarios 4 and 5, where we changed the response simulation:
	$y_i \sim \mathcal{B}(1, [\exp (\x_i \tr \bbeta) + \kappa]/
	[\exp (\x_i \tr \bbeta) + 1 + \kappa])$ as in \cite{komori_asymmetric_2016}, 
	where the link function is unbalanced for $\kappa \neq 0$. We use 
	$\kappa \in \{ 0.1, 0.5, 1 \}$, which leads to 6 different simulations 
	from Scenarios 4 and 5 in total. We present the results in Figures
	\ref{fig:lines2_simulations_res6_auc_briers}-
	\ref{fig:lines2_simulations_res11_auc_briers}. From the Figures we see that 
	\texttt{gren} outperforms the regular elastic net even with a misspecified 
	link function in terms of AUC. For the Brier skill score there seems to be 
	some detrimental effect of the misspecification.

>>>>

  \subsection{Model misspecification}\label{sec:modelmisspecification}
  To assess the effects of model misspecification we conducted a series of 
  simulations under different modes of misspecification and simulation settings.
  We investigate model misspecification by comparing \texttt{gren} to the
  regular elastic net.
  To investigate the effect of misspecifying the link function, we simulated
  according to Scenarios 4 and 5, where we changed the response simulation:
	$y_i \sim \mathcal{B}(1, [\exp (\x_i \tr \bbeta) + \kappa]/
	[\exp (\x_i \tr \bbeta) + 1 + \kappa])$ as in \cite{komori_asymmetric_2016}, 
	where the link function is unbalanced for $\kappa \neq 0$. We use 
	$\kappa \in \{ 0.1, 0.5, 1 \}$, which leads to 6 different simulations 
	from Scenarios 4 and 5 in total. We present the results in Figures
	\ref{fig:lines2_simulations_res6_auc_briers}-
	\ref{fig:lines2_simulations_res11_auc_briers}. From the Figures we see that 
	\texttt{gren} outperforms the regular elastic net even with a misspecified 
	link function in terms of AUC. For the Brier skill score there seems to be 
	some detrimental effect of the misspecification.
